### 2022-05-17 paper/introduction.tex
update paper 1. add related works
1. add model: ng + resnet 2. update paper

%% add noise image
\begin{figure}[!h]
	\centering
	\begin{tikzpicture}
		\node[inner sep=0pt] (depthmap) at (0,0)
		{\includegraphics[width=.5\textwidth]{./pic/00028.normal0.png}};
	\end{tikzpicture}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%% talk about the reason of this thesis %%%%%%%%%%%%%%%%%%

%% standard method for normal inference is insufficient, input is sparse, not robust enough
Standard methods compute normals from point cloud using neighboring information in image space or use Shape from Shading. However, the point clouds captured by sensors like Kinect or similar RGB-D, LiDAR sensors are only semi-dense. As shown in Figure \ref{fig:standard_normal_inference}. If map these normals to mesh, that is not good at all. Standard methods dependents on chosen neighbor size, if too small, it has larger noise sensitive, if too large, the output will too smooth and not crispy. Errors may occur in regions with inter-reflections, where we have errors in the 3D measurement.

%% add noise image
\begin{figure}[!h]
	\centering
	\begin{tikzpicture}

		\node[inner sep=0pt] (depthmap) at (0,0)
		{\includegraphics[width=.3\textwidth]{./pic/00028.depth0.png}};

		\path [line] (3,0) -- node [text width=1.5cm,midway,above ] {SVD/PCA} (5,0);

		\node[inner sep=0pt] (normal) at (8,0)
		{\includegraphics[width=.3\textwidth]{./pic/00028.normal0.png}};
	\end{tikzpicture}
\caption{Left: Depth Map, Right: Semi-dense Normal Map}
\label{fig:standard_normal_inference}
\end{figure}

%% there exists space for improvment 
Although the depth image is incomplete, the depth sensor usually able to capture grayscale texture image, which are typically fully dense due to their passive nature. Furthermore, if the texture image is already illuminated by strong directional light of a video projector, whose position is known, then there should exist theoretical relations between light direction, normal direction, etc. Thus the normal can be inferenced better using the given image information and depth map.

%%%%%%%%%%%%%%%%%%% talk about the chanllege of this task %%%%%%%%%%%%%%%%%%
Both depth and grayscale image are initially relevant to the machine learning algorithms. Based grayscale image and corresponding semi-dense depth map, a CNN model can be designed to inference the normal map, which gives more density and robust comparing to standard algorithm. However, the missing pixels in depth map can be distributed around the whole image, some of the region leaves complete empty pixels. This situation imposes further processing for the missing regions and some other challenges on the machine learning methods. 
In this thesis, we found a solution for the problems mentioned above.

%% improved normal inference figure
\begin{figure}[!h]
	\centering
	\begin{tikzpicture}

		\node[inner sep=0pt] (image) at (0,0)
		{\includegraphics[width=.2\textwidth]{./pic/00028.image0.png}};

		\node[text width=1cm] at (2,0) {$ + $};

		\node[inner sep=0pt] (depthmap) at (3.3,0)
		{\includegraphics[width=.2\textwidth]{./pic/00028.depth0.png}};
		\node[text width=1cm] at (8,0) {$ ? $};

		\path [line] (5,0) -- node [text width=1cm,midway,above ] {CNN} (6,0);

	\end{tikzpicture}
	\caption{Left: Grayscale Image, Middle: Depth Map}
	\label{fig:improved_normal_inference}
\end{figure}

### 2022-05-17 paper/related_work.tex
1. add model: ng + resnet 2. update paper

In order to estimate normals of an object surface.

@@

In 2018, Yu et al. \cite{gconv} presented a CNN based method with guided

@@

\section{Sparse Input processing}
%% gconv, nconv, median filter...
The depth-map captured by active sensors are usually full with missing pixels and holes. Thus a preprocessing for the depth map is necessary before it is fed into a neural network.

Generally, it can be solved as image inpainting problems.\cite{inpainting1},\cite{inpainting2}. Recently, some deep learning based method for image inpainting achieved quite good performance for the hole mending task. 
Notably, in 2016, Oord et al. \cite{gated_activation} proposed a gated activation unit for a CNN model,
\[\textbf{y} = \tanh (W_{k,f} * \textbf{x}) \odot \sigma (W_{k,g} * \textbf{x})\]
to substitute the standard activation layer, where $ \sigma $ is the sigmoid function, which constricts the output value of second part between $ [0,1] $.  The function is inspired by Long Short-Term Memory (LSTM) \cite{lstm} and Rated Recurrent Unit (GRU).\cite{gru} It is originally used for learning complex interactions as LSTM gates does. In 2018, Yu et al. \cite{gconv} employed same function for free-form image inpainting, which can be used to learn mask automatically from image it self.

Different to aforementioned approaches, Knutsson et al. in 2005 introduced normalized convolution \cite{nconv} dealing with missing sample case for convolution operation. 
In 2018, Eldesokey et al. \cite{ncnn} applied normalized convolution in CNN as normalized convolution layer that takes both sparse depth map and a binary confidence map as input to perform scene depth completion.  
In 2020, Eldesokey et al. \cite{pncnn} focus on modeling the uncertainty of depth data instead of assuming binary input confidence.

>>>>

\section{Sparse Input processing}

%% methods deal with sparse input, like nconv, gconv ...
The depth map is supposed to be dense. Therefore, how to accept sparse depth map as input in CNNs is one of the most important problem. Some trivial solutions like median filters are good enough, if the missing pixels are sparse enough, however, for the case of huge missing holes in the depth map, it produces just a paltry result. Thus a reasonable guess is required for missing areas. Generally, it can be solved as image inpainting problems,\cite{inpainting1},\cite{inpainting2}.

%% Deep learning based approaches
Some deep learning based method for image inpainting also achieved quite good performance for the hole mending task. 
%% talk about gconv
Notably, in 2016, Oord et al. \cite{gated_activation} proposed a gated activation unit for a CNN model,
\[\textbf{y} = \tanh (W_{k,f} * \textbf{x}) \odot \sigma (W_{k,g} * \textbf{x})\]
to substitute the standard activation layer, where $ \sigma $ is the sigmoid function, which constricts the output value of second part between $ [0,1] $.  The function is inspired by Long Short-Term Memory (LSTM) \cite{lstm} and Rated Recurrent Unit (GRU).\cite{gru} It is originally used for learning complex interactions as LSTM gates does. In 2018, Yu et al. \cite{gconv} employed same function for free-form image inpainting, which can be used to learn mask automatically from image it self.

%% talk about nconv
Different to aforementioned approaches, Knutsson et al. in 2005 introduced normalized convolution \cite{nconv} dealing with missing sample case for convolution operation, which aims to reconstruct the missing pixels from the sparse output sensed by cameras, which particularly considered the confidence of each interpolated pixels, since it provides the trustworthiness of the predicted value. The higher the reliability of the value inference, the better the model shape reconstruction.

In 2018, Eldesokey et al. \cite{ncnn} applied normalized convolution in CNN as normalized convolution layer that takes both sparse depth map and a binary confidence map as input to perform scene depth completion.
In 2020, Eldesokey et al. \cite{pncnn} focus on modeling the uncertainty of depth data instead of assuming binary input confidence.

%% normal estimation method introduction
Ideally, the normal of each pixel in the depth map can be calculated based on its neighbor pixels constructing a over-determined function systems and solving by algebra methods\cite{geometry_based_solution}. This approach gives a quick but coarse normal inference. It also can be predict directly by feeding the image directly into a CNN \cite{Eigen}, in this case, no depth map is required.
GeoNet\cite{GeoNet} integrates both ideas to refine the coarse normal map with another CNN predicted normal map. 
%% traditional methods

@@

In 2018, Yu et al. \cite{gconv} presented a CNN based method with gated convolutional layer.

In 2018, Hua et al. \cite{guided} presented an approach integrating color image and certainty map into the network to enhance the performance of depth map density.

@@

%% CNN based methods
The deep convolutional neural network is typically used for image classification, which achieved great success in last several years. \cite{yolov3}, \cite{efficientDet}.

%% talk about the reason we need new type of network architecture
These kinds of network architecture takes a single image as input which usually employed for classification problems. The image is usually convoluted with convolutional layer and downsampling with pooling layers. The outputs of the network consists of a single value to represent the ID of corresponding class \cite{efficientDet}, or with set of values to represent the position of bounding boxes.\cite{yolov3}.

However, in many other vision tasks, the output is demanded as an image, instead of predicting one or several classes of the input, but the classes of each pixel are predicted. In this case, the traditional network architecture is not suitable anymore.

%% talk about image upsampling, unet
Recently, Ronneberger et al proposed an architecture called UNet \cite{unet} for biomedical image segmentations. The architecture is shown in Figure \ref{fig:u-net}.The first half network is a usual classification convolutional network, the second half replace the pooling layers to upsampling layers, thus in the end of the second half, the output is back to the input size. The proposed network can successfully assigned each pixel a class for segmentation tasks. Under this symmetric network, an input image is downsampled 3 times and upsampled 3 times. Output image has exactly the same size as input image. The downsampling and upsampling both have large number of feature channels, which guarantee the network propagates the information to higher resolution layers.

\begin{figure}[!h]
	\centering
	\includegraphics[width=\textwidth]{./ref/u-net-illustration-correct-scale2}
	\caption{U-net architecture (example for 32x32 pixels in the lowest resolution). Each blue box corresponds to a multi-channel feature map. The number of channels is denoted on top of the box. The x-y-size is provided at the lower left edge of the box. White boxes represent copied feature maps. The arrows denote the different operations.
	}
	\label{fig:u-net}
\end{figure}

%% guided scene completion
